MWA tied-array processing III: Microsecond time resolution via a synthesis filter

### 2019-10-22 ipfb.tex
Added a paragraph about 'critically sampled' in the MWA implementation section.

The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of a tap, i.e. $N$ samples.
This implies that each coarse channel sample becomes part of the input (i.e. a term in the sum) for $P$ consecutive fine channel samples.
However, it should be noted that there is no redundant information.
The term ``critically'' sampled is justified by noting that the downsampling by a factor of \dots inherent in the PFB algorithm is exactly balanced by the

The above specifications yield a specific frequency response, as explained in the preceding section.
The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq. \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$. The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.

>>>>

The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of one tap, i.e. $N = 128$ samples.
This implies that each coarse channel sample becomes part of the input (i.e. a term in the sum) for $P$ consecutive fine channel samples.
The term ``critically'' sampled is justified by noting that the downsampling by a factor of $P$ (inherent in the PFB algorithm) is exactly counterbalanced by the inclusion of each coarse channel sample in $P$ distinct output channels, with a different weighting (filter coefficient and phase term) applied in each case.
As discussed below, the fact that the PFB is critically sampled greatly informs the design of the synthesis filter used to reconstruct the coarse channel samples from the fine channels.

The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq. \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$. The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}, and the fact that the PFB is critically sampled.
